\documentclass[11pt]{article}
\usepackage{titling}
\usepackage[english]{babel}
\usepackage[margin=0.6in]{geometry} % Page Dimension

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                PACKAGES                %  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Styling Choices
\setlength{\parskip}{\baselineskip}%

% Math
\usepackage{amsmath, amsthm, amssymb}
\usepackage[inline]{asymptote}
\usepackage{xcolor}
\usepackage{cancel}

% Allows for hyperlinking
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=magenta,
}

% Blind Footnote
\newcommand\blfootnote[1]{%
  \makeatletter{\footnotetext{#1}\makeatother}
}

% Fancy Header
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Kalda Mechanics}
\rhead{\thepage}

% Coloured Boxes
\usepackage{xcolor}
\definecolor{border}{HTML}{004D4D}
\definecolor{hard}{HTML}{ffccb3}
\definecolor{easy}{HTML}{b3e6b3}
\definecolor{normal}{HTML}{f2f2f2}

% Syntax: \colorboxed[<color model>]{<color specification>}{<math formula>}
\newcommand*{\colorboxed}{}
\def\colorboxed#1#{%
  \colorboxedAux{#1}%
}
\newcommand*{\colorboxedAux}[3]{%
  % #1: optional argument for color model
  % #2: color specification
  % #3: formula
  \begingroup
    \colorlet{cb@saved}{.}%
    \color#1{#2}%
    \boxed{%
      \color{cb@saved}%
      #3%
    }%
  \endgroup
}

% Setup Gray Solution Boxes
\usepackage[breakable,many]{tcolorbox}
\newtcolorbox[auto counter]{solution}[1]{
    enhanced, breakable,
    arc=0pt,
    % colback=default, % Background color
    colframe=white, % Border Color
    coltitle=black, % Title Color
    fonttitle=\bfseries,
    title=\fcolorbox{border}{#1}{\textcolor{border}{pr} \bfseries \textcolor{border}{\thetcbcounter}.},
    attach title to upper,
    after title={\ },
    segmentation style={dashed, gray},
}

% Title and front page
\title{Solutions to Problems in Mechanics Handout by Jaan Kalda With detailed diagrams and walkthroughs}
% Author
\author{\textsc{Ashmit Dutta, QiLin Xue, Kushal Thaman, Arhaan Ahmad}}

\begin{document}
\begin{titlepage}
    \begin{center}
        \vspace*{1cm}
 
        \Huge
        \textbf{Solutions to Jaan Kalda's Problems in Mechanics}
 
        \vspace{0.5cm}
        \LARGE
        \textbf{With detailed diagrams and walkthroughs}
        
        \vspace{0.1cm}
        Edition 1.2.2
        
        \vspace{1.2cm}
 
         Ashmit Dutta, QiLin Xue, Kushal Thaman, Arhaan Ahmad
        \vspace{10mm}
 \begin{center}
\begin{asy}
import olympiad;
size(11cm);
label("N", (1.38, 1.3), NE);
label("$\mu N$", (0.25, 1.15), NW);
label("O", (0,0), W);
label("A", (0.2, 0.2), N);
label("$\theta$", (0.7868, 0.5), 2SW);
label("$\alpha$", (-0.05, -0.6), SE);
label("$\beta$", (0.7, -2.3), N);

draw(circle((0,0), 1), linewidth(1.5pt));
filldraw(circle((0.2, 0.2), 0.72), gray(0.9));
dot((0,0));
dot((0.2,0.2));
draw((0.25, -0.954)--(0.7868, -3), linewidth(1.5pt));
filldraw(circle((0.7868,-3), 0.1), black);
draw((0,0)--(0,-3), dashed);
draw((0,0)--(0.7868, -3));
draw((0.2,0.2)--(0.7868,-3), dotted);
draw((0.7868, 0.6172)--(0.7868, -3), dashed);
draw((0, 0)--(0.7868, 0.6172));
draw((0.7868, 0.6172)--(0.25, 1.15), arrow=Arrow(4));
draw((0.7868, 0.6172)--(1.38, 1.3), arrow=Arrow(4));
draw((0.7868, 0.6172)--(0.7868, 1.8), arrow=Arrow(4));
label("Q", (0.7868, 1.8), N);

pair A,B,C,D,E,F,G, H;
B = (0.7868, -3);
A = (0,0);
C = (0.2, 0.2);
D = (0, -3);
E = (0.7868, 2.1);
F = (-0.5, 1.9);
G = (0.7868, 0.6172);
H = (0.7868, -3);
markscalefactor=0.05;
draw(anglemark(E, G, F, 4));
draw(anglemark(A, G, H, 4));
markscalefactor=0.1;
draw(anglemark(D, A, B, 4));
draw(anglemark(G, H, A, 4));
\end{asy}
\end{center}
        \vfill
        
        \Large
        Updated
        \today
 
    \end{center}
\end{titlepage}
\newpage
%%%%%%%%%%%
% Preface %
%%%%%%%%%%%
\section*{Preface}
\vspace{-5mm}
\indent Jaan Kalda's \href{https://www.ioc.ee/~kalda/ipho/}{handouts} are beloved by physics students both in for a quick challenge, to students preparing for international Olympiads. As of writing, the current \href{https://www.ioc.ee/~kalda/ipho/meh_ENG2.pdf}{mechanics} handout (ver 1.2) has 86 unique problems and 74 main `ideas'.

This solutions manual came as a pilot project from the online community at \url{artofproblemsolving.com}. Although there were detailed hints provided, full solutions have never been written. The majority of the solutions seen here were written on a private forum given to those who wanted to participate in making solutions. In an amazing show of an online collaboration, students from around the world came together to discuss ideas and methods and created what we see today.

This project would not have been possible without the countless contributions from members of the community. Online usernames were used for those who did not wish to be named: 

\textit{Heramb Podar, Ameya Deshmukh, Viraj Jayam, Rakshit, dbs27, Anant Lunia, Jai, Sean Chen, Ayon Ghosh, Joshua S, Tarun Agarwal, c\_deng}
\subsection*{Structure of The Solutions Manual}
\vspace{-5mm}
Each chapter in this solutions manual will be directed towards a section given in Kalda's mechanics handout. There are three major chapters: statics, dynamics, and revision problems. If you are stuck on a problem, cannot make progress even with the hint, and come here for reference, look at only the start of the solution, then try again. Looking at the entire solution wastes the problem for you and ruins an opportunity for yourself to improve.

\subsection*{Contact Us}
\vspace{-5mm}
Despite editing, there is almost zero probability that there are \textit{no} mistakes inside this book. If there are any mistakes, you want to add a remark, have a unique solution, or know the source of a specific problem, then please contact us at \url{hello@physoly.tech}. The most current and updated version can be found on our website \url{physoly.tech}

Please feel free to contact us at the same email if you are confused on a solution. Chances are that many others will have the same question as you.

\newpage
\section{Solutions to Statics Problems}
\vspace{-5mm}
This section will consist of the solutions to problems from problem 1-23 of the handout. Statics is typically the analysis of objects not in motion. However, objects travelling at constant velocity or with a uniform acceleration can be treated as a statics problem with a frame of reference change. This usually involves balancing forces, torques, and more to achieve equilibrium. 

\input{P01}
\input{P02}
\input{P03}
\input{P04}
\input{P05}
\input{P06}
\input{P07}
\input{P08}
\input{P09}
\input{P10}
\input{P11}
\input{P12}
\input{P13}
\input{P14}
\input{P15}
\input{P16}
\input{P17}
\input{P18}
\input{P19}
\input{P20}
\input{P21}
\input{P22}
\input{P23}

\newpage
\section{Solutions to Dynamics Problems}

This chapter will focus on problems 24-55 of the handout. Dynamics, unlike statics, analyzes the motion of objects in motion. Lots of dynamics problems require analyzing the accelerations of the system or finding the forces acting in a system. In this section, Prof Kalda introduces a technique called Lagrangian formalism that is used to find the acceleration of a object in a system using the generalized coordinate $\xi$. We are also introduced to the majority of mechanics problems in this section of the handout.

\input{P24}
\input{P25}
\input{P26}
\input{P27}
\input{P28}
\input{P29}
\input{P30}
\input{P31}
\input{P32}
\input{P33}
\input{P34}
\input{P35}
\input{P36}
\input{P37}
\input{P38}
\input{P39}
\input{P40}
\input{P41}
\input{P42}
\input{P43}
\input{P44}
\input{P45}
\input{P46}
\input{P47}
\input{P48}
\input{P49}
\input{P50}
\input{P51}
\input{P52}
\input{P53}
\input{P54}
\input{P55}

\newpage
\section{Solutions to Revision Problems}
This section will contain problem 55-86 of the handout. Revision problems take concepts and ideas from earlier problems and places them in a new context. As a result, many of the problems in this section will seem familiar. This however, does not mean that all the problems in this section are easy. Some of the hardest problems originate in this section.

\input{P56}
\input{P57}
\input{P58}
\input{P59}
\input{P60}
\input{P61}
\input{P62}
\input{P63}
\input{P64}
\input{P65}
\input{P66}
\input{P67}
\input{P68}
\input{P69}
\input{P70}
\input{P71}
\input{P72}
\input{P73}
\input{P74}
\input{P75}
\input{P76}
\input{P77}
\input{P78}
\input{P79}
\input{P80}
\input{P81}
\input{P82}
\input{P83}
\input{P84}
\input{P85}
\input{P86}

\end{document}
